220410_Competition

### 2023-08-14 code/analysis.Rmd
updates

## Again, with did2s
```{r}
did2s(
      data = df.spill2 , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 0 | Zip + Year + D, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )

>>>>

## Again, with did2s
```{r}
did2s(
      data = df.spill2 %>% inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
               select(`Grant Number`, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")), 
      yname = "Total.z", 
      treatment = "Tx",
        first_stage = ~ 0 | Zip + Year + D + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )

### 2023-08-14 code/analysis_Redo.Rmd
updates

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
               select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
  select(Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR) %>% 
  mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
  unique()

@@

did2s(
      data = df.sum ,#%>% filter(ZipFilter == 2), 
      yname = "Altmans.Z", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

df.sum <- df.qual.exp %>% #filter(`Grant Number` != "H80CS00225") %>% 
  ungroup() %>% 
  #rename(`Grant Number` = Grant.Number, `Surplus as a pct of before dep expenses` = Surplus.as.a.pct.of.after.dep.expenses) %>% 
  #filter(MarketShare < 0.4) %>%  #median(MarketShare, na.rm = TRUE) - 0.25
  #inner_join(df.qual.exp %>% filter(Year == 2015 & Total < 15000) %>% select(`Grant Number`), by = c("Grant Number")) %>%  #& Zips < 1.75 or 7.75
  select(`Grant Number`, Year, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Total, IMM2yo:DepScrn) %>%
  # inner_join(df.qual.exp %>% filter(Year == 2015) %>%
  #                                           mutate(ZipFilter = ifelse(Total < 12000, 1,
  #                                                              ifelse(Total > 12000, 2, NA))) %>% select(`Grant Number`, ZipFilter), by = c("Grant Number")) %>%
  inner_join(df.qual.exp %>% filter(Year == 2016) %>% #mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% 
               select(`Grant Number`, ZipFilter, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("Grant Number")) %>% 
  select(`Grant Number`, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z, Pct.HTN.CNTRL, Pct.NHA:Pct.Children, MCD, COM, MCR, Total, IMM2yo:DepScrn) %>% 
  mutate(Tx = ifelse(Year >= Att & Att > 0, 1, 0)) %>% 
  unique() %>% 
  mutate(NewQuality = (CRC + ChildBMI + AdultBMI + Tobac + DepScrn) / 5)

@@

did2s(
      data = df.sum ,#%>% filter(ZipFilter == 2), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > quantile(ds, 0.5, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 1),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom), by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
      yname = "Altmans.Z", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )

### 2023-08-14 code/data_cleaning.Rmd
adding covariates and streamlining analysis
updated code
updates

library(gridExtra)
library(cowplot)
library(Matching)
library(fixest)
library(directlabels)

@@

compare <- read.csv("comeptition.data.final.csv")[,-1]
colnames(compare) <- cnames

>>>>

library(gridExtra)
library(cowplot)
library(Matching)
library(fixest)
library(directlabels)
library(did2s)

@@

compare <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_processed/comeptition.data.final.csv")[,-1]
colnames(compare) <- cnames
